Self Regulation Ontology Retest Data Report

### 2017-04-16 SRO_Report.Rmd
begun adding the completion time analyses

```{r}
match_t1_t2 <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id'){
  df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var)
  df = df %>% 
    na.omit()%>%
    gather(dv, score, -sub_id) %>%
    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
    select(-drop)
   return(df)
}

@@

>>>>

```{r}
match_t1_t2 <- function(dv_var, t1_df = retest_subs_test_data, t2_df = retest_data, merge_var = 'sub_id', format = "long"){
  df = merge(t1_df[,c(merge_var, dv_var)], t2_df[,c(merge_var, dv_var)], by = merge_var)

  df = df %>% 
    na.omit()%>%
    gather(dv, score, -sub_id) %>%
    mutate(time = ifelse(grepl('\\.x', dv), 1, ifelse(grepl('\\.y', dv), 2, NA))) %>%
    separate(dv, c("dv", "drop"), sep='\\.([^.]*)$') %>%
    select(-drop)

  if(format == 'wide'){
    df = df%>% spread(time, score) 
  }

  return(df)
}

@@

## Completion times

Do people differ in how much their scores change depending on how many days it has been since they completed the initial battery?

Make data frame with standardized difference between two scores for each measure for each subject.

```{r}
t1_2_difference = data.frame()

for(i in 1:length(numeric_cols)){
  tmp = match_t1_t2(numeric_cols[i],format='wide')
  tmp = tmp %>% 
    mutate(difference = scale(`2` - `1`))
  t1_2_difference = rbind(t1_2_difference, tmp)
}

str(as.data.frame(t1_2_difference$difference))
```

Add completion dates to this data frame.

```{r}
disc_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/discovery_completion_dates.csv', header=FALSE)
val_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/validation_completion_dates.csv', header=FALSE)
test_comp_date = rbind(disc_comp_date, val_comp_date)
rm(disc_comp_date, val_comp_date)
retest_comp_date = read.csv('/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-21-2017/Local/retest_completion_dates.csv', header=FALSE)
comp_dates = merge(retest_comp_date, test_comp_date, by="V1")
names(comp_dates) <- c("sub_id", "retest_comp", "test_comp")
comp_dates$retest_comp = as.Date(comp_dates$retest_comp)
comp_dates$test_comp = as.Date(comp_dates$test_comp)
comp_dates$days_btw = with(comp_dates, retest_comp-test_comp)

t1_2_difference = merge(t1_2_difference, comp_dates[,c('sub_id', 'days_btw')], by='sub_id')
```

The effect of number of days in between in the full model you'd want (potentially even including the interaction between the fixed effects)

```{r eval = FALSE}
mod = lmer(difference ~ dv + days_btw + (1|sub_id), data = t1_2_difference)

mod_fixed = as.data.frame(fixef(mod))
mod_fixed["days_btw",]
```

Does average standardized difference change with number of days between completion?

```{r}
tmp = t1_2_difference %>%
  group_by(sub_id) %>%
  summarise(mean_diff = mean(difference, na.rm=T),
            days_btw = unique(days_btw))

length(unique(tmp$mean_diff))
str(as.data.frame(t1_2_difference$difference))

tmp %>%
  ggplot(aes(days_btw, mean_diff))+
  geom_point()+
  theme_bw()
```

Box plots showing the distribution of difference scores for each task

```{r}
t1_2_difference %>%
  ggplot(aes(dv, difference))+
  geom_boxplot()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
